Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-11-12 manuscript/manuscript.tex
Fix editor's remark 7

We define an external computation point $P(r, \phi, \lambda)$ in a geocentric spherical
coordinate system at a radius $r$, geocentric latitude $\phi$, and longitude $\lambda$
where the gravitational fields are going to be calculated.
The first- and second-order derivatives of the gravitational potential are taken with
respect to the local north-oriented Cartesian coordinate system of $P$
(Fig.~\ref{fig:tesseroid}).
\citet{Grombein2013} provide efficient formulations for the volume integrals of the
gravitational potential and its first- and second-order derivatives of a tesseroid with
homogeneous density.
Here, we will assume that the tesseroid has a density varying with $r$ according to an
arbitrary function $\rho(r)$.
Thus, the integrals for the gravitational fields are slightly modified to

@@

\iftwocol{
\begin{equation}
    \begin{split}
        \iiint\limits_\Omega \rho(r') f(r', \phi', \lambda')
        d\Omega \approx& \\
        A
        \sum\limits_{i=1}^{N^r}
        \sum\limits_{j=1}^{N^\phi}
        \sum\limits_{k=1}^{N^\lambda}
        & W_i^r W_j^\phi W_k^\lambda \rho(r_i) f(r_i, \phi_j, \lambda_k),
    \end{split}
\label{eq:glq-var-dens}
\end{equation}
}{
\begin{equation}
    \iiint\limits_\Omega \rho(r') f(r', \phi', \lambda') d\Omega \approx
    A
    \sum\limits_{i=1}^{N^r}
    \sum\limits_{j=1}^{N^\phi}
    \sum\limits_{k=1}^{N^\lambda}
    W_i^r W_j^\phi W_k^\lambda \rho(r_i) f(r_i, \phi_j, \lambda_k),
\label{eq:glq-var-dens}
\end{equation}
}

@@

\noindent $(r_i, \phi_j, \lambda_k)$ are the quadrature nodes, and $W_i^r$ are the
quadrature weights.

>>>>

Consider an arbitrary tesseroid in a geocentric spherical coordinate system defined by
pairs of geocentric latitudinal ($\phi_1$, $\phi_2$), longitudinal ($\lambda_1$,
$\lambda_2$) and radial ($r_1$, $r_2$) boundaries.
We define an external computation point $P(r, \phi, \lambda)$ located at radius $r$,
geocentric latitude $\phi$, and longitude $\lambda$ where the gravitational fields the
tesseroid generates are going to be calculated.
The first- and second-order derivatives of the gravitational potential are taken with
respect to the local north-oriented Cartesian coordinate system of $P$
(Fig.~\ref{fig:tesseroid}).
\citet{Grombein2013} provide efficient formulations for the volume integrals of the
gravitational potential and its first- and second-order derivatives of a tesseroid with
homogeneous density.
Here, we will assume that the tesseroid has a density varying with $r$ according to an
arbitrary function $\rho(r)$.
Thus, the integrals for the gravitational fields are slightly modified to

@@

\iftwocol{
\begin{equation}
    \begin{split}
        \int\limits_{\lambda_1}^{\lambda_2}
        \int\limits_{\phi_1}^{\phi_2}
        \int\limits_{r_1}^{r_2}
        \rho(r') f(r', \phi', \lambda')
        dr' d\phi' d\lambda' \approx& \\
        A
        \sum\limits_{i=1}^{N^r}
        \sum\limits_{j=1}^{N^\phi}
        \sum\limits_{k=1}^{N^\lambda}
        W_i^r W_j^\phi W_k^\lambda
        &\rho(r_i) f(r_i, \phi_j, \lambda_k),
    \end{split}
\label{eq:glq-var-dens}
\end{equation}
}{
\begin{equation}
    \int\limits_{\lambda_1}^{\lambda_2}
    \int\limits_{\phi_1}^{\phi_2}
    \int\limits_{r_1}^{r_2}
    \rho(r') f(r', \phi', \lambda')
    dr' d\phi' d\lambda' \approx
    A
    \sum\limits_{i=1}^{N^r}
    \sum\limits_{j=1}^{N^\phi}
    \sum\limits_{k=1}^{N^\lambda}
    W_i^r W_j^\phi W_k^\lambda \rho(r_i) f(r_i, \phi_j, \lambda_k),
\label{eq:glq-var-dens}
\end{equation}
}

@@

\noindent $f(r', \phi', \lambda')$ are the non-density dependent portion of the
integration kernels, $(r_i, \phi_j, \lambda_k)$ are the quadrature nodes, and $W_i^r$
are
the quadrature weights.
